Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-09-11 main.tex
more text

\section{Reflection on shellable stars}\label{section:extension}

This section is devoted to a crucially important geometric construction. 
Suppose that we have a shellable simplicial complex. 
Every time we add a simplex according to the shelling sequence, 
we complete the local star of the some simplex in the triangulation (see Lemma~\ref{lemma:existenceofstar}).
We will need a homeomorphism from the new simplex on its complement in the newly completed star.
This homeomorphism is required to preserve the interface and to be bi-Lipschitz.
We are particularly interested in the norms of its Jacobian.

@@

\begin{remark}
    While the reflection mapping and its analysis in Theorem~\ref{theorem:starreflection} serve our purpose,
    it might be possible to improve the estimate with an improved analysis or construction.
\end{remark}

>>>>

\section{Reflections and Deformations on shellable stars}\label{section:extension}

This section is devoted to crucially important geometric constructions. 
Suppose that we have a shellable simplicial complex. 
Every time we add a simplex according to the shelling sequence, 
we complete the local star of the some simplex in the triangulation (see Lemma~\ref{lemma:existenceofstar}).
We will need a homeomorphism from the new simplex on its complement in the newly completed star.
This homeomorphism is required to preserve the interface and to be bi-Lipschitz.
We are particularly interested in the norms of its Jacobian.

This reflection will be used subsequently to generalize the discussion in Section~\ref{section:gradient}
to the setting of differential forms. 
In addition to that, this endeavor will also produce another geometric tool 
which enables an additional possibility to estimate Poincar\'e--Friedrichs constants:
we construct a deformation which maps the entire star into the complement of the newly completed star. 
Again, we give explicit estimates of the Jacobian.

@@

\begin{remark}
    We notice that the mappings $\Xi_{1}$ and $\Xi_{2}$ above are not only bi-Lipschitz, but in fact also piecewise affine, 
    where piecewise refers to an essentially non-overlapping decomposition of their respective domains into convex polytopes.
    While the reflection and deformation mappings in Theorem~\ref{theorem:starreflection} serve our purpose,
    it might be possible to improve the estimate with an improved analysis or construction.
\end{remark}
